### 2023-03-24 resilience.tex
Up

\begin{theorem}\label{k-down-up}
Let $\mathscr{S}=(S,\rightarrow, \leq)$ be a completion-post-effective $\omega^2$-WSTS with strong compatibility and the predbasis hypothesis, and two finite sets: $\Bad$ and $\Safe$.
The  $k$-resilience problem (kRP) is decidable for $k \geq K$. \textcolor{red}{CONJECTURE for now}
 \end{theorem}

\begin{proof}
To decide the kRP, we may compare the input $k$ with $K$. If $k \geq K$, we conclude that is %uniformely 
$k$-resilient; 
if $k < K$ we cannot answer. if moreover $\mathscr{S}=(S,\rightarrow, \leq)$ has the predbasis hypothesis, we may compute the least $n$ such that $ \uparrow \pred^n(\Safe)=  \uparrow \pred^*(\Safe)$. $S$ is %uniformely
 $k$-resilient iff $n \leq k$ \alain{hum...mais il peut y avoir des chemins plus courts}and then kRP is decidable.
\end{proof}

>>>>

\begin{theorem}\label{k-down-up}
Let $\mathscr{S}=(S,\rightarrow, \leq)$ be a completion-post-effective $\omega^2$-WSTS with strong compatibility% and the predbasis hypothesis
, and two finite sets: $\Bad$ and $\Safe$.
The  $k$-resilience problem (kRP) is decidable for $k \geq K$. 
% \textcolor{red}{CONJECTURE for now}
 \end{theorem}

\begin{proof}
To decide the kRP, we may compare the input $k$ with $K=max(k_a \mid a=1,..,m \times n)$.
	If $k \geq K$, we conclude that 
$k$-resilience holds.
	If $k < K$, then we can answer the question by checking every paths of length smaller
	than $K$ from the $J_i$ in the completion.
\end{proof}
